
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Govind Tomar} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} {+91 98706 63286}
    $|$
    \faAt \hspace{.5pt} \href{mailto:govindtomar94@gmail.com}{govindtomar94@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/govindtomar94/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/404fixer}{Github}
    $|$
    
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
{Indian Institute of Information Technology Sonepat (IIIT Sonepat)
}{Sonepat, India}
{Bachelor of Technology in Computer Science;   \textbf{CGPA: 8.8/10}}{Aug. 2019 \textbf{--} Jul. 2023}


  \resumeSubHeadingListEnd


%----------- PROJECTS -----------

\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeProjectHeading
{\textbf{ResumeBuilder} $|$ \underline{\emph{\href{https://github.com/404fixer/ResumeBuilder}{GitHub}}} $|$ \underline{\emph{\href{https://localhost:3000}{Project Link}}}} {}
      \resumeItemListStart
      \resumeItem{Built a web app using which users can make beautiful latex-like resumes within 5 minutes.}\resumeItem{Featured with authentication, authorization, 7 different sectioned resume template, view and download resume in PDF format, and get LaTex code.}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{SyncM} $|$ \underline{\emph{\href{https://github.com/404fixer/SyncM-Speaker}{GitHub}}} $|$ \underline{\emph{\href{https://sync--m.herokuapp.com/}{Project Link}}}} {}
      \resumeItemListStart
      \resumeItem{Build a Web App using which you can play the same music across different devices at the same time to boost the audio and give the experience of external speakers without actually having them.}\resumeItem{Built it using socket.io (for real-time, bidirectional event-based communication), express, and nodeJS.}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{Sparsh Beauty Parlour} $|$ \underline{\emph{\href{https://github.com/404fixer/sparsh-beauty-parlour}{GitHub}}} $|$ \underline{\emph{\href{http://sparsh-beauty-parlour.herokuapp.com/}{Project Link}}}} {}
      \resumeItemListStart
      \resumeItem{Designed and Developed a Web App for a Local Beauty Parlour to showcase their work and book an appointment.}\resumeItem{Technologies used HTML, CSS, JavaScript, Bootstrap, nodeJS, and nodemailer (which allows sending emails from nodeJS).}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{RGB Color Guessing Game} $|$ \underline{\emph{\href{https://github.com/404fixer/webDevLearningProject/tree/master/colorGameProject}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Developed a game of guessing the colour (from the given visual colour options) by looking at the RGB code of it.}\resumeItem{Built it using HTML, CSS, and Vanilla JavaScript.}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{Obtained Global Rank 518 in Facebook Hacker Cup Qualification Round 2021. $|$ \underline{\emph{\href{https://drive.google.com/file/d/1jPu8BfnQKZ1c27xlJ-RbH9h47UY2SjvW/view}{Link}}}}\resumeItem{Obtained Global Rank 99 in Codechef C.O.D.E.R.S. 2021. $|$ \underline{\emph{\href{https://www.codechef.com/rankings/FOUR21B?order=asc&search=govindtomar21&sortBy=rank}{Link}}}}\resumeItem{Obtained Global Rank 126 in Codechef December Lunchtime 2021. $|$ \underline{\emph{\href{https://www.codechef.com/rankings/LTIME103B?order=asc&search=govindtomar21&sortBy=rank}{Link}}}}\resumeItem{Obtained Global Rank 473 in Codeforces Round 762 (Div. 3). $|$ \underline{\emph{\href{https://codeforces.com/contest/1619/standings?list=da8ee0f7b6c9d6b336f1c30139f022f7}{Link}}}}\resumeItem{Obtained Global Rank 1566 in Google Kickstart Round E 2021. }\resumeItem{Obtained Global Rank 2087 in ICPC Amritapuri 2020 Preliminary Round. }\resumeItem{Obtained 97.9999637 percentile in JEE Main 2018 among a million candidates across the country. }
  \resumeItemListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

  
    \textbf{Languages:}{ C, C++, JavaScript, Java, Python} \ \vspace{3pt}

    \textbf{Developer Tools:}{ Git, and GitHub} \ \vspace{3pt}

    \textbf{Operating Systems:}{ macOS, Windows, Ubuntu} \ \vspace{3pt}

    \textbf{Development:}{ HTML, CSS, SASS, JavaScript, jQuery, ExpressJS, MongoDB, Firebase, nodeJS, ReactJS} \ \vspace{3pt}

    \textbf{Miscellaneous:}{ Data Structure and Algorithms, Competitive Programming, Web Development} \ \vspace{3pt}

}}
\resumeSubHeadingListEnd



%----------- Profiles -----------

\section{Profiles}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{\underline{\href{https://codeforces.com/profile/govindtomar}{Codeforces}}}\resumeItem{\underline{\href{https://www.codechef.com/users/govindtomar21}{Codechef}}}\resumeItem{\underline{\href{https://atcoder.jp/users/404fixer}{Atcoder}}}
  \resumeItemListEnd

%-------------------------------------------
\end{document}
